Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex

The property framework has many parameters to support broad applicability.
Conceptually, the following steps are needed to instantiate the framework to a specific machine
and code style: (i) define the base machine semantics; (ii) distinguish payload
from enforcement parts (if any) of the machine state; (iii) identify the set of
security-relevant operations and rules required by the code style; (iv) determine
how to label (or otherwise associate) machine instruction with security-relevant
operations as appropriate; (v) specify the form of observable events.

In \cref{sec:example} we give such an instantiation, and use it to explain the
security properties.  But we stress that the property definitions themselves
are \emph{independent} of the parameter instantiation.

\apt{Suggest moving threat model to here.}

>>>>

\proposecut{Our property framework has many parameters to support broad applicability.}
Conceptually, the following steps are needed to instantiate the framework to a specific machine
and code style: (i) define the base machine semantics; (ii) distinguish payload
from enforcement parts (if any) of the machine state; (iii) identify the set of
security-relevant operations and rules required by the code style; (iv) determine
how to label (or otherwise associate) machine instruction with security-relevant
operations as appropriate; (v) specify the form of observable events.

\bcp{cut this?}In \cref{sec:example} we give such an instantiation, and
  use it to illustrate our security properties.  But we stress that
  the property definitions themselves are independent of the
  instantiation.

\apt{Suggest moving threat model to here.}\bcp{Fine.}
